\begin{longtable}{p{0.14\textwidth}p{0.24\textwidth}p{0.18\textwidth}p{0.16\textwidth}p{0.18\textwidth}}
\caption{Chain-of-Custody Confidence Matrix}\label{tab:chain-of-custody}\\
\toprule
ID & Item & Discovery & Custody & Gaps \\
\midrule
\endfirsthead
\toprule
ID & Item & Discovery & Custody & Gaps \\
\midrule
\endhead
PE-0001 & Body of unknown male found at Somerton Beach near seawall/opposite Somerton Crippled Children's Home. & Found about 7 a.m. on 1948-12-01; evening observations at 7 p.m. and about 7:30 p.m. on 1948-11-30. & Fragmentary & Exact body recovery log, burial/remains chain, and current official records. \\
PE-0002 & Partly smoked cigarette located between/right cheek and right lapel or on right collar area. & Observed at body location morning of 1948-12-01; evening witness said no cigarette in raised hand. & Fragmentary & Was it collected; was brand or saliva/fingerprint examined; relation to body cigarette packet? \\
PE-0003 & Clothing worn by deceased: coat, shoes, shirt, pullover, jockey underpants, singlet, socks, trousers and one tie. & On body at Somerton Beach. & Fragmentary & Exact clothing list, garment measurements, present status, destruction/loss record. \\
PE-0004 & Tie worn by deceased and two ties in suitcase, one bearing the name T. Keane. & Body tie on deceased; suitcase ties recovered from luggage. & Fragmentary & Which tie carried which name/mark; did any survive? \\
PE-0005 & Shoes worn by deceased. & On body. & Fragmentary & Exact make, size, sole wear, photographs, survival status. \\
PE-0006 & Socks worn by deceased. & On body. & Fragmentary & Exact sock type/condition; whether vegetation retained. \\
PE-0007 & Removed/missing tags or labels from clothing and suitcase articles. & Observed on body clothing and suitcase items. & Fragmentary & Which labels were removed, when, by whom; whether any threads/remnants survive. \\
PE-0008 & Single uncancelled second-class Adelaide-to-Henley Beach railway ticket. & Found in clothing search on body. & Fragmentary & Exact ticket serial; current status; purchaser unknown. \\
PE-0009 & Municipal Tramways Trust bus ticket, 7d ticket tied to Holdernesse route/journal. & Found in clothing search on body. & Fragmentary & Exact serial; holder identity; boarding/alighting location. \\
PE-0010 & Army Club cigarette packet containing Kensitas cigarettes. & Found on body per Leane/Moss inventory. & Fragmentary & Was mismatch investigated; exact count; survival status. \\
PE-0011 & Bryant and May matches box, about one quarter full per Leane OCR. & Found on body. & Fragmentary & Exact match count/condition; survival status. \\
PE-0012 & Two combs / metal comb reported in body property. & Found on body. & Fragmentary & Exact type/manufacturer; survival status. \\
PE-0013 & Juicy Fruit chewing gum packet, about half full per Leane OCR. & Found on body. & Fragmentary & Exact quantity/packaging; survival status. \\
PE-0014 & Tamam Shud paper slip found in concealed trouser fob pocket. & Found in fob pocket of trousers; not found during initial Moss search; found some time afterwards. & Fragmentary & Exact discovery date/time; original survival; paper match to recovered Rubaiyat; current custodian. \\
PE-0015 & Rubaiyat copy/reference book associated with Tamam Shud comparison. & Brown compared slip to bookshop/library copies; coroner associated slip with a second edition Fitzgerald Rubaiyat. & Fragmentary & Exact recovery, owner/finder, edition, tear-match, current status. \\
PE-0016 & Rubaiyat code/markings image preserved as SM-code\_full\_res.jpg. & Original code context not established from DOC-0001 testimony used in Mission 9. & Fragmentary & Original document provenance; relation to associated Rubaiyat; handwriting/code analysis deferred. \\
PE-0017 & Suitcase found unclaimed at Adelaide Railway Station luggage/cloak room. & Located by Leane in unclaimed luggage on 1949-01-14; taken into police possession on 1949-01-19. & Fragmentary & Current status/destruction authority; full inventory; original photographs. \\
PE-0018 & Railway Station luggage ticket no. 52703 for suitcase, issued 1948-11-30 between 11 a.m. and noon per North. & Produced by Harold North; associated with unclaimed suitcase. & Fragmentary & Exact ticket number; retained half; depositor identity. \\
\bottomrule
\end{longtable}
