% Auto-generated Mission 6 table. Update CSV first.
\begin{longtable}{p{0.11\textwidth}p{0.18\textwidth}p{0.20\textwidth}p{0.13\textwidth}p{0.28\textwidth}}
\caption{Mission 6 Exhibit Index}\\
\toprule
ID & Evidence & Description & Pages & Uncertainties \\
\midrule
\endfirsthead
\toprule
ID & Evidence & Description & Pages & Uncertainties \\
\midrule
\endhead
EXH-0001 & EV-0008 & Railway ticket from Adelaide to Henley Beach / ticket marked in testimony & pp.21,75 & Exact exhibit number OCR uncertain; purchaser unknown. \\
EXH-0002 & EV-0009 & Municipal Tramways Trust bus ticket, serial/punch identified & pp.21,23,25 & Holder not identified; exact boarding/alighting unknown. \\
EXH-0003 & EV-0012; EV-0013; EV-0010; EV-0011 & Packet containing cigarettes, matches, combs, chewing gum and other body-pocket articles, marked Exhibit C.1 & p.21 & Exact packet contents require full visual/manual transcript. \\
EXH-0004 & EV-0016 & Teeth chart, marked Exhibit C.2 & pp.35,39 & Exact chart annotations need non-OCR visual transcription. \\
EXH-0005 & N/A & Extract, marked Exhibit C.3 & p.39 & OCR does not identify extract; manual page check required. \\
EXH-0006 & EV-0003 & Luggage ticket for suitcase, marked Exhibit C.4 in OCR & pp.53,57 & OCR exhibit number distorted; exact ticket number requires visual check. \\
EXH-0007 & EV-0005 & Body photographs, marked C.5-C.8 in OCR & p.63 & Exact exhibit numbers and photograph set need visual confirmation. \\
EXH-0008 & EV-0015 & Fingerprints/fingerprint records of deceased & pp.63,67 & Full circulation log missing. \\
EXH-0009 & EV-0001 & Tamam Shud paper slip, marked Exhibit C.9 in OCR & pp.5,57,71,73,81 & Exact finder/date and paper provenance unresolved. \\
EXH-0010 & EV-0003 & Photographs of suitcase/case, marked Exhibits C.10-C.14 in OCR & p.75 & Need image/transcript confirmation. \\
EXH-0011 & EV-0005 & Clothing found on body, marked Exhibit C.15 & p.77 & Exact item list and later custody unknown. \\
EXH-0012 & EV-0003 & Suitcase found at station, marked Exhibit C.16 & p.77 & Exact current status unknown. \\
EXH-0013 & EV-0007 & Bust/cast made from body, marked Exhibit C.17 & pp.27,77 & Exact custody and preservation status unknown. \\
EXH-0014 & EV-0017 & Biological specimens: stomach contents, liver/muscle, urine, blood & p.47 & Exact lab notes and retained sample status unknown. \\
EXH-0015 & EV-0002 & Rubaiyat copy/reference book used for Tamam Shud comparison & pp.5,71,73 & Exact recovery and owner of associated Rubaiyat copy unresolved. \\
\bottomrule
\end{longtable}
