\begin{longtable}{p{0.16\textwidth}p{0.23\textwidth}p{0.19\textwidth}p{0.14\textwidth}p{0.18\textwidth}}
\caption{Forensic Identifiers}\label{tab:forensic-identifiers}\\
\toprule
ID & Type & Description & Source & Limitations \\
\midrule
\endfirsthead
\toprule
ID & Type & Description & Source & Limitations \\
\midrule
\endhead
FID-0001 & dental chart & Dwyer prepared a missing-teeth chart; separate chart reproduction preserved as DOC-0017. & John Matthew Dwyer; DOC-0017 & Chart image has no OCR and exact dental notation needs specialist/manual transcription. \\
FID-0002 & dental characteristics & Several teeth missing; Dwyer stated missing teeth would be noticeable if the man laughed but not necessarily if speaking. & John Matthew Dwyer & No comparative dental records acquired. \\
FID-0003 & fingerprints & Fingerprint chart of deceased male found at Somerton; separate visual reproduction preserved. & DOC-0016 & Image quality moderate; fingerprint classification annotations need specialist review. \\
FID-0004 & fingerprints & Durham fingerprinted deceased and circulated copies to Australian states, New Zealand and important overseas bureaus. & Patrick James Durham & Full bureau response file not acquired. \\
FID-0005 & photographs & Durham produced full-face and side-face photographs marked as exhibits. & Patrick James Durham & Original photos/exhibit images not fully catalogued in Mission 8. \\
FID-0006 & death mask/bust & Lawson made a cast of the features; bust was later marked as exhibit C.17. & Paul Francis Lawson; Raymond Lionel Leane & Embalming/formalin and postmortem changes limit living-appearance inference. \\
FID-0007 & physical measurements & Height/build not precisely measured in extracted medical pages; described as tallish and in good physical condition. & John Matthew Dwyer & Need autopsy sheet or police physical description for exact measurements. \\
FID-0008 & scars/marks & Light scar on left upper arm; uncertain vaccination mark; two recent right-hand abrasions noted. & John Matthew Dwyer; John Burton Cleland & No complete body map acquired. \\
FID-0009 & biological samples & Stomach contents, liver/muscle, urine and blood were submitted to Cowan. & Robert James Cowan & Physical sample retention/disposal unknown. \\
FID-0010 & death certificate & Certified copy records unidentified male body and death registration details. & Registrar of Births, Deaths and Marriages & OCR is poor; visual certificate review needed before exact transcription. \\
\bottomrule
\end{longtable}
