\begin{longtable}{p{0.16\textwidth}p{0.23\textwidth}p{0.19\textwidth}p{0.14\textwidth}p{0.18\textwidth}}
\caption{Selected Forensic-Medical Observations}\label{tab:medical-observations}\\
\toprule
ID & Category & Observation & Source & Confidence \\
\midrule
\endfirsthead
\toprule
ID & Category & Observation & Source & Confidence \\
\midrule
\endhead
MED-0001 & external body condition & Tallish male, estimated about 45 years, greying hair and good physical condition. & John Matthew Dwyer p.35 & High \\
MED-0002 & external body condition & Fingernails and feet appeared cared for; nails carefully trimmed. & John Matthew Dwyer p.35 & High \\
MED-0003 & injuries/trauma & No external markings of note recorded by Dwyer. & John Matthew Dwyer p.35 & High \\
MED-0004 & lividity/rigor & Postmortem rigidity described as intense; deep lividity noted behind/above ears and neck. & John Matthew Dwyer p.35 & High \\
MED-0005 & anatomical identifiers & Several teeth were missing; Dwyer prepared a missing-teeth chart. & John Matthew Dwyer p.35; DOC-0017 & High \\
MED-0006 & external body condition & Pupils were small, unusual/uneven in outline, and about the same size. & John Matthew Dwyer p.35 & Moderate \\
MED-0007 & external body condition & Small patch of dried saliva was noted at the right of the mouth. & John Matthew Dwyer p.35 & High \\
MED-0008 & external body condition & Sand was in the hair but not in nostrils or mouth. & John Matthew Dwyer p.37 & High \\
MED-0009 & internal pathology & Scalp, skull and brain were normal except small brain vessels were readily visible with congestion. & John Matthew Dwyer p.37 & High \\
MED-0010 & internal pathology & Pharynx was congested; gullet showed superficial whitening and a patch of ulceration. & John Matthew Dwyer p.37 & High \\
MED-0011 & stomach contents & Stomach deeply congested with superficial redness and small submucosal haemorrhages. & John Matthew Dwyer p.37 & High \\
MED-0012 & stomach contents & Blood was mixed with food in the stomach. & John Matthew Dwyer p.37; p.39; p.43 & High \\
MED-0013 & organ congestion & Kidneys, liver, lungs, spleen and brain/upper vessels were described with congestion or engorgement. & John Matthew Dwyer pp.37-39 & High \\
MED-0014 & heart findings & Heart was normal in size and otherwise normal; muscle was tough/firm; heart was if anything contracted. & John Matthew Dwyer p.37 & High \\
MED-0015 & internal pathology & Spleen described as strikingly large and firm, about three times normal size. & John Matthew Dwyer p.37 & High \\
MED-0016 & stomach contents & Food in stomach estimated by Dwyer as present up to 3 or 4 hours before death, with anxiety caveat. & John Matthew Dwyer p.37 & Moderate \\
MED-0017 & internal pathology & Microscopy showed destruction of centres of liver lobules; otherwise congestion signs predominated. & John Matthew Dwyer p.39 & Moderate \\
MED-0018 & uncertainty & Dwyer stated death was not natural and immediate cause was heart failure, but he could not state what caused heart failure. & John Matthew Dwyer p.39 & High \\
\bottomrule
\end{longtable}
