% Auto-generated Mission 7 table. Update CSV first.
\begin{longtable}{p{0.10\textwidth}p{0.16\textwidth}p{0.16\textwidth}p{0.18\textwidth}p{0.11\textwidth}p{0.21\textwidth}}
\caption{Mission 7 Movement Reconstruction}\\
\toprule
ID & Date/Description & Time/Recovery & Location/Evidence & Confidence & Uncertainty \\
\midrule
\endfirsthead
\toprule
ID & Date/Description & Time/Recovery & Location/Evidence & Confidence & Uncertainty \\
\midrule
\endhead
MOV-0001 & 1948-11-30 & 06:15-14:00 & Adelaide Railway Station ticket box: Henley Beach rail ticket was issued during ticket clerk Douglas George Townsend shift window. & High & Ticket purchaser not identified; exact issue time unknown; does not prove deceased personally bought ticket. \\
MOV-0002 & 1948-11-30 & 11:15 a.m. route departure & Adelaide-Somerton bus route from Railway Station toward St Leonards: Bus ticket associated with body was issued on route departing Railway Station at about 11.15 a.m. & High & Ticket holder not identified; boarding and alighting locations not established. \\
MOV-0003 & 1948-11-30 & Between bus arrival and 7:00 p.m. & Somerton Beach area: Coroner recorded no one came forward to say the man was seen at Somerton during this interval. & Moderate & Negative evidence only; depends on completeness of witness canvass. \\
MOV-0004 & 1948-11-30 & 7:00 p.m. & Somerton Beach near steps/seawall: A man was seen lying where body was later found and raising his right arm before it fell. & High & Witness did not see face; identity of man as deceased not conclusively established. \\
MOV-0005 & 1948-11-30 & About 7:20-8:00 p.m. & Somerton Beach near same location: Strapps and Neill observed a man lying at the beach and did not see movement. & High & Night/dusk observation; identity not established; observations limited. \\
MOV-0006 & 1948-12-01 & About 2:00 a.m. estimated & Unknown: Dr Bennett estimated death could have occurred around about 2:00 a.m. or up to eight hours before 9.40 a.m. examination. & Moderate & Medical estimate only; place of death unknown; not a movement directly observed. \\
MOV-0007 & 1948-12-01 & About 6:35-6:45 a.m. & Somerton Beach: Beach witness saw activity near body after morning swim and then communicated with Constable Moss; Moss proceeded to beach after telephone message. & High & First witness name and exact telephone/report sequence require manual page confirmation. \\
MOV-0008 & 1948-12-01 & About 7:00 a.m. & Somerton Beach: Body of unknown man found on shore at Somerton. & Very High & Exact first-discovery witness details require manual confirmation. \\
MOV-0009 & 1948-12-01 & After police attendance; exact time unknown & Somerton Beach to Royal Adelaide Hospital to City Mortuary: Body was conveyed by police ambulance to Royal Adelaide Hospital, where life was pronounced extinct, then later conveyed to City Mortuary. & High & Exact transfer times not indexed. \\
MOV-0010 & 1948-12-02 & 7:30 a.m. & City Mortuary: Dwyer performed postmortem examination on body pointed out as found at Somerton. & High & Medical details require manual transcription and visual confirmation. \\
MOV-0011 & 1949-01-14 and 1949-01-19 & Unknown & Adelaide Railway Station luggage office: Leane saw unclaimed suitcase on 14 January and took possession on 19 January. & High & Exact chain of custody after police possession unresolved. \\
\bottomrule
\end{longtable}
