\begin{longtable}{p{0.14\textwidth}p{0.24\textwidth}p{0.18\textwidth}p{0.16\textwidth}p{0.18\textwidth}}
\caption{Selected Physical Evidence Catalogue}\label{tab:physical-evidence-catalogue}\\
\toprule
ID & Item & Source & Custody & Confidence \\
\midrule
\endfirsthead
\toprule
ID & Item & Source & Custody & Confidence \\
\midrule
\endhead
PE-0001 & Body of unknown male found at Somerton Beach near seawall/opposite Somerton Crippled Children's Home. & DOC-0001 pp.5,15-21,27,35,63,67,93. & Fragmentary & High for discovery and initial movement; Moderate for full preservation history. \\
PE-0002 & Partly smoked cigarette located between/right cheek and right lapel or on right collar area. & DOC-0001 pp.5,17,19,21. & Fragmentary & Moderate \\
PE-0003 & Clothing worn by deceased: coat, shoes, shirt, pullover, jockey underpants, singlet, socks, trousers and one tie. & DOC-0001 pp.5,21,57,59,61,71,77,79,81. & Fragmentary & High for existence; Moderate for item-level details. \\
PE-0004 & Tie worn by deceased and two ties in suitcase, one bearing the name T. Keane. & DOC-0001 p.57. & Fragmentary & Moderate \\
PE-0005 & Shoes worn by deceased. & DOC-0001 pp.27,57,79,81. & Fragmentary & High for existence and condition observations. \\
PE-0006 & Socks worn by deceased. & DOC-0001 pp.57,79,81. & Fragmentary & Moderate \\
PE-0007 & Removed/missing tags or labels from clothing and suitcase articles. & DOC-0001 pp.5,7,59,61,81. & Fragmentary & Moderate \\
PE-0008 & Single uncancelled second-class Adelaide-to-Henley Beach railway ticket. & DOC-0001 pp.5,21,75. & Fragmentary & High \\
PE-0009 & Municipal Tramways Trust bus ticket, 7d ticket tied to Holdernesse route/journal. & DOC-0001 pp.5,21,23,25. & Fragmentary & High \\
PE-0010 & Army Club cigarette packet containing Kensitas cigarettes. & DOC-0001 pp.21,57. & Fragmentary & Moderate \\
PE-0011 & Bryant and May matches box, about one quarter full per Leane OCR. & DOC-0001 pp.21,57. & Fragmentary & Moderate \\
PE-0012 & Two combs / metal comb reported in body property. & DOC-0001 pp.5,21,57. & Fragmentary & Moderate \\
PE-0013 & Juicy Fruit chewing gum packet, about half full per Leane OCR. & DOC-0001 pp.5,21,57. & Fragmentary & Moderate \\
PE-0014 & Tamam Shud paper slip found in concealed trouser fob pocket. & DOC-0001 pp.5,57,71,73,81. & Fragmentary & High for existence; Moderate for custody. \\
PE-0015 & Rubaiyat copy/reference book associated with Tamam Shud comparison. & DOC-0001 pp.5,71,73. & Fragmentary & Moderate \\
PE-0016 & Rubaiyat code/markings image preserved as SM-code\_full\_res.jpg. & DOC-0012 / SM-code\_full\_res.jpg; source register lead. & Fragmentary & Moderate for digital preservation; Low for original custody. \\
\bottomrule
\end{longtable}
