% Auto-generated Mission 7 table. Update CSV first.
\begin{longtable}{p{0.10\textwidth}p{0.16\textwidth}p{0.16\textwidth}p{0.18\textwidth}p{0.11\textwidth}p{0.21\textwidth}}
\caption{Mission 7 Possession Inventory}\\
\toprule
ID & Date/Description & Time/Recovery & Location/Evidence & Confidence & Uncertainty \\
\midrule
\endfirsthead
\toprule
ID & Date/Description & Time/Recovery & Location/Evidence & Confidence & Uncertainty \\
\midrule
\endhead
POS-0001 & Clothing worn by deceased: coat, shoes, shirt, pullover, jockey underpants, singlet, socks, trousers, tie & Body / clothing search and Leane testimony & EV-0005; EXH-0011 & High & Exact item list and exhibit numbering require visual confirmation; later custody unknown. \\
POS-0002 & Single uncancelled Adelaide-to-Henley Beach railway ticket & Found on body/clothing search & EV-0008; EXH-0001 & High & Purchaser and exact issue time unknown. \\
POS-0003 & Municipal Tramways Trust bus ticket & Found on body/clothing search & EV-0009; EXH-0002 & High & Holder, boarding point and alighting point unknown. \\
POS-0004 & Cigarettes/cigarette packet and partly smoked cigarette near body/face & Body/clothing and scene observation & EV-0012; EV-0014; EXH-0003 & Moderate & Brand/container details need manual confirmation; half-smoked cigarette collection status unclear. \\
POS-0005 & Matches box & Found on body/clothing search per inventory testimony & EV-0013; EXH-0003 & Moderate & Exact quantity and preservation status unknown. \\
POS-0006 & Combs / metal comb & Found on body/clothing search & EV-0010; EXH-0003 & Moderate & Exact count/type requires visual confirmation. \\
POS-0007 & Juicy Fruit chewing gum packet & Found on body/clothing search & EV-0011; EXH-0003 & Moderate & Exact quantity/status unknown. \\
POS-0008 & Tamam Shud paper slip & Found later in trouser fob pocket & EV-0001; EXH-0009 & High & Exact discovery date/time and current custodian unknown; intent not established. \\
POS-0009 & Brown suitcase and contents & Unclaimed luggage at Adelaide Railway Station; seen 14 Jan and taken 19 Jan per Leane & EV-0003; EXH-0012 & High & Full inventory and custody after police possession need manual transcription. \\
POS-0010 & Suitcase clothing/textiles including dressing gown, laundry bag, singlets, underpants, shirt, handkerchiefs, scarf, towel and related items & Suitcase inventory per Leane testimony & EV-0003; EV-0004; EV-0005; EXH-0012 & Moderate & OCR distortion likely; complete inventory needs manual transcription. \\
POS-0011 & Tools/personal articles in suitcase: scissors, razor strop, lighter, razor, shaving brush, screwdriver, pencils, toothbrush/paste, dish, soap dish and small items & Suitcase inventory per Leane testimony & EV-0003; EXH-0012 & Moderate & OCR distortion likely; exact item list needs manual transcription. \\
POS-0012 & Orange/tan thread and mending materials & Suitcase and clothing comparison testimony & EV-0003; EV-0005; EXH-0012 & Moderate & Thread color/material comparison needs visual/manual confirmation. \\
POS-0013 & Fingerprints/fingerprint chart & Fingerprinting by Durham; separate chart reproduction acquired & EV-0015; EXH-0008 & High & Full circulation log and original chart custody unknown. \\
POS-0014 & Body photographs / identification photographs & Photographed by Durham at City Morgue & EV-0005; EXH-0007 & High & Exact exhibit numbers and image set need visual confirmation. \\
POS-0015 & Death mask/bust/cast & Made by Lawson at City Mortuary on 7 June 1949 & EV-0007; EXH-0013 & High & Current status and sampling/custody history unknown. \\
POS-0016 & Biological specimens: stomach contents, liver/muscle, urine, blood & Received by Cowan on 2 Dec 1948 from P.C. Sutherland & EV-0017; EXH-0014 & High & Exact lab notes, retention and disposal unknown. \\
\bottomrule
\end{longtable}
