\begin{longtable}{p{0.16\textwidth}p{0.23\textwidth}p{0.19\textwidth}p{0.14\textwidth}p{0.18\textwidth}}
\caption{Toxicology Issues Mentioned in Primary Evidence}\label{tab:toxicology}\\
\toprule
ID & Substance/Class & Mentioned By & Status & Limitation \\
\midrule
\endfirsthead
\toprule
ID & Substance/Class & Mentioned By & Status & Limitation \\
\midrule
\endhead
TOX-0001 & Common poisons & Robert James Cowan & Not detected & Exact analytical methods and full panel unknown. \\
TOX-0002 & Cyanides & Robert James Cowan; John Burton Cleland & Not detected & No specific cyanide method recorded in acquired text. \\
TOX-0003 & Alkaloids & Robert James Cowan; John Burton Cleland & Not detected & Specific alkaloids and methods not listed. \\
TOX-0004 & Barbiturates & John Matthew Dwyer; Robert James Cowan; John Burton Cleland; Cedric Stanton Hicks & Considered but unproven & Decomposition/non-detection debated; no laboratory detail. \\
TOX-0005 & Soluble hypnotic & John Matthew Dwyer & Suggested by witness & Class not defined in extracted testimony. \\
TOX-0006 & Carbolic acid & Robert James Cowan & Not detected & Specific test not recorded. \\
TOX-0007 & Morphine & Cedric Stanton Hicks & Ruled unlikely & Chemical name OCR around passage distorted but morphine is readable. \\
TOX-0008 & Insulin & John Matthew Dwyer; John Burton Cleland; Cedric Stanton Hicks & Ruled unlikely & No retained sample/lab method documented; injection mark could be missed. \\
TOX-0009 & Diphtheria toxin & John Matthew Dwyer & Suggested by witness & No test recorded. \\
TOX-0010 & Botulism toxin & John Matthew Dwyer & Ruled unlikely & No test recorded. \\
TOX-0011 & Nicotine & John Matthew Dwyer & Not detected & Specific nicotine method not recorded. \\
TOX-0012 & Aconite/aconitine class & John Matthew Dwyer & Considered but unproven & OCR damaged; exact name requires confirmation. \\
TOX-0013 & Curare/tubarine & John Matthew Dwyer; John Burton Cleland & Considered but unproven & Injection route and detection limitations unresolved. \\
TOX-0014 & Unspecified cardiac glycoside/drug group & Cedric Stanton Hicks; coroner remarks & Suggested by witness & Names and methods unavailable in current OCR; official transcript/visual transcription needed. \\
\bottomrule
\end{longtable}
