% Auto-generated Mission 6 table. Update CSV first.
\begin{longtable}{p{0.11\textwidth}p{0.18\textwidth}p{0.20\textwidth}p{0.13\textwidth}p{0.28\textwidth}}
\caption{Mission 6 Witness Index}\\
\toprule
ID & Name & Role & Pages & Summary \\
\midrule
\endfirsthead
\toprule
ID & Name & Role & Pages & Summary \\
\midrule
\endhead
WIT-0001 & Name not legible in OCR & Beach witness / Somerton resident & pp.15-17 & Reported seeing a man lying near the steps on the evening of 30 November and later communicating with Constable Moss after seeing the body next morning. \\
WIT-0002 & John Moss & Police constable / first responding police witness & pp.19-21 & Described attending Somerton Beach after a telephone message, body position, cigarette near collar/cheek, lack of visible violence, transport to Royal Adelaide Hospital and City Morgue, and initial property search. \\
WIT-0003 & Edmund Leslie Hall & Municipal Tramways Trust claims officer assistant & p.23 & Identified bus ticket as MTT ticket issued by conductor Holdernesse on 30 November 1948 on route departing Railway Station at 11.15 a.m. \\
WIT-0004 & Arthur Anzac Holdernesse & Tram/bus conductor & p.25 & Stated he had no independent recollection of the November trip apart from records/log and Hall statement. \\
WIT-0005 & Paul Francis Lawson & Taxidermist / cast maker & pp.27-29 & Described making a mould and cast of the deceased features at the City Mortuary on 7 June 1949 and observations about body/feet. \\
WIT-0006 & Gordon Kenneth Strapps & Evening beach witness & pp.31-33 & Reported arriving at Somerton about 7.20 or 7.30 p.m. on 30 November with Miss Neill, seeing a man lying on the beach, and observing no movement before leaving around 8 p.m. \\
WIT-0007 & John Matthew Dwyer & Medical witness / postmortem examiner & pp.35-45 & Described postmortem examination at City Mortuary at 7.30 a.m. on 2 December 1948, external observations, organ congestion, stomach contents, and medical opinion. \\
WIT-0008 & Robert James Cowan & Deputy Government Analyst & pp.47-49 & Received stomach contents, liver/muscle, urine and blood on 2 December 1948 and tested for common poisons without detecting any. \\
WIT-0009 & Olive Constance Neill & Evening beach witness & p.51 & Was with Strapps on evening 30 November, saw a person on beach, thought something might be wrong, did not see legs move, and remarked the man might be dead. \\
WIT-0010 & Harold Rolfe North & Senior porter / cloak room witness & pp.53-55 & Produced luggage ticket associated with suitcase; stated ticket was issued 30 November 1948 at 11 a.m. stamp window and suitcase remained unclaimed. \\
WIT-0011 & Raymond Lionel Leane & Detective / police investigator & pp.57-69; p.77 & Described identification inquiries, clothing and body property, suitcase recovery on 14/19 January, contents, removed tags, weather, circulation of description/fingerprints/photos, and recalled exhibit custody. \\
WIT-0012 & Patrick James Durham & Police photographer and fingerprint expert & p.63 & Photographed body full face and side face, fingerprinted deceased, circulated photographs/fingerprints, and photographed paper found on deceased. \\
WIT-0013 & William West & South Australian Railways employee & p.65 & Gave train arrival/departure times for 30 November 1948 including Melbourne Express and Henley Beach departures. \\
WIT-0014 & Leonard Douglas Brown & Detective / police investigator & pp.71-73 & Compared clothing in suitcase/body, reported sand in trouser cuffs, received Tamam Shud slip from Leane, made bookshop/library inquiries about Rubaiyat text and meaning. \\
WIT-0015 & Douglas George Townsend & Ticket clerk & p.75 & Stated he issued the Henley Beach ticket on 30 November during his 6.15 a.m. to about 2 p.m. shift and could not remember purchaser. \\
WIT-0016 & John Burton Cleland & Medical witness / pathology professor & pp.79-89 & Compared clothing and suitcase contents, thread, tags, cleanliness, body condition, and gave medical opinion regarding unnatural death/poison possibilities. \\
WIT-0017 & Cedric Stanton Hicks & Professor of Physiology and Pharmacology & pp.91-101 & Reviewed medical facts and Dwyer/Bennett evidence; discussed possible poison groups and timing difficulties. \\
WIT-0018 & John Barkly Bennett & Medical witness who examined body & p.93 & Examined body at 9.40 a.m. on 1 December 1948 in police ambulance outside Adelaide Hospital and estimated death could have occurred up to eight hours earlier. \\
\bottomrule
\end{longtable}
